\section{Implementation}
We have implemented our live programming methodology as a plugin
for Javascript programming in the Atom text editor~\cite{Atom}.
While a programmer writes code in the main panel,
live debugging information is shown in a side panel.
By manipulating the output value,
the programmer can make use of programming by example.

\subsection{Live Debugging}
As users write code, we continually run the code on the given inputs.
As Javascript is an interpreted language, this is straightforward.
Unfortunately, the process of editting code often involves that code
being in a malformed, syntatically invalid state.
Thus, we only update the displayed output when the code is, in fact,
syntatically vaild.~\bill{Is this actually the behavior?}
When the user closes the file or editor,
we write the examples to a metadata file.
We reload the examples when the file is opened again.

\subsection{Programming by Example}
When a user modifies an examples output, we update the code to reflect the change.
To synthesize code, we make use of CVC4's Syntax-guided synthesis (or SyGuS) algorithm~\cite{reynolds2017sygus}.
SyGuS is an approach that performs an enumerative search over the space of possible programs,
based on a given grammar.
We draw possible grammatical elements from the existing function implementation.
This both helps ensure that the newly generated code does not stray too far from the programmers original implementation,
and helps constraint the space CVC4 has to search over.
If we fail to find a solution to the SyGus problem, we iteratively increase the size of the grammar~\bill{Mark, more about how this is done?}.
